Generating Images from Captions\\ with Attention

### 2015-11-06 iclr-paper-new.tex
changed task of in itself to task in itself

\subsubsection{Comparison With Other Models}
\vspace{-0.05in}
Quantitatively evaluating generative models remains a challenging task in of itself as each method of evaluation suffers from its own specific drawbacks. Compared to reporting classification accuracies in discriminative models, the measures defining generative models are intractable most of the times and might not correctly define the real quality of the model. To get a better comparison between performances of different generative models, we report results on two different metrics as well as a qualitative comparison of different generative models.

>>>>

\subsubsection{Comparison With Other Models}
\vspace{-0.05in}
Quantitatively evaluating generative models remains a challenging task in itself as each method of evaluation suffers from its own specific drawbacks. Compared to reporting classification accuracies in discriminative models, the measures defining generative models are intractable most of the times and might not correctly define the real quality of the model. To get a better comparison between performances of different generative models, we report results on two different metrics as well as a qualitative comparison of different generative models.
